Scalar and Representative Observables for Polarimetric SAR Data

### 2013-09-30 paper_dev/article_pp.tex
abc d

\section{Discussion}

\subsection{Validating the proposed models against real-life data}
\label{sec:polsar_models_validation}

This section aims to verify the theoretical models given in Eqns. \ref{eqn:determinant_distribution} and \ref {eqn:determinant_ratio_distribution} against practical data.
Both of these models require the estimation of two parameters from some given captured data.
They are the dimensional number $d$ and the look number $L$.
The dimensional number $d$ is related to the type of (POL)SAR data,
  with $d=1,2,3$ corresponding to the cases of SAR, partial and full polarimetric SAR data, respectively.
The look-number $L$ can be taken either as nominally stated by the data provider,
  or it can be estimated using the technique proposed by \cite{Anfinsen_2009_TGRS_3795}.
To show the robustness of the proposed models, their validation is also put to test on different types of POLSAR sensors.
Specifically in this article, the air-borne four-look ($L=4$) AIRSAR image of Flevoland and
  a fine-quad single-look complex RADARSAT2 image ($L=1$) are employed.
Since the determinant of the covariance matrix is only significant on multi-look data,
  nine-look processing is first applied on the single-look RADARSAT2 data ($L=9$).

Since it has been shown in Section \ref{sec:sar_special_case_of_polsar} that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
  which have been validated extensively, the validation of the proposed $d=1$ model is quite straightforward. %only a simple validation is presented for this case.  
Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the results of an experiment carried out for the stated purpose.
In the experiment, the intensity of single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
The histograms for both the intensity and intensity ratio (TODO:Replot) %the log-distance and contrast
  are then plotted against the theoretical PDF given above.
The plots are obtained with ENL set to both the nominal number of 4 and the estimated number of (TODO:CALC).
Also presented are the plots of the same experiment applied on a homogeneous patch inside the nine-look processed RADARSAT2 image (TODO:NewPlot).
In this case, even though the RADARSAT2 has a nominal look-number of 9, its ``true'' value is estimated as $L=$ (TODO:CALC).
In all cases, good visual match is apparent, which validates the model proposed above. %providing us a simple validation of the result.

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH) determinant]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_determinant}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH) determinant]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_determinant}
	} \\
	\subfloat[AIRSAR (HH) determinant ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH) determinant ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	} \\
	\subfloat[AIRSAR (HH) change ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH) change ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{The specific d=1 models are validated on both practical RADARSAT2 and AIRSAR datasets}
\label{fig:verify_det_ratio_model_1D}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_determinant}
	} 
	\hfill	
	\subfloat[AIRSAR (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}
	\hfill	
	\subfloat[AIRSAR (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}  \\
	\subfloat[RADARSAT2 (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_determinant}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{The specific d=1 models are validated on both practical RADARSAT2 and AIRSAR datasets}
\label{fig:verify_det_ratio_model_1D}
\end{figure}
%endif

The remainder of this section now focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
Similar experiments like the one described for SAR data is carried out
  for both types of polarimetric SAR
  on both AIRSAR and RADARSAT2 datasets.
The look-number is estimated for each type of data and for each image using the technique described in \cite{Anfinsen_2009_TGRS_3795} and is also noted in the plots.

@@

Intuitively, the concept of the determinant being representative of the POLSAR data can be thought of as being similar to the concept of using the magnitude as being representative of a complex number
(in a sense this is also why intensity is widely considered representative of the SAR data complex).
Similar to the determinant, the magnitude observable is also scalar and is not lossless.
To fully represent the complex number, another observable is needed besides the magnitude.
The magnitude however is much more widely used, as it can be shown that its is invariant to a change in the reference frame.
Similarly, the determinant of the POLSAR covariance matrix is also scalar and invariant to a change of polarization basis.
Thus while it is not fully representative of the POLSAR data, it can be said to be highly representative of it.
The important thing is that, it can be used to give a scalar comparison of the multi-dimensional data.
This is also similar to the standard use of the magnitude when two or more complex numbers are to be compared. %, most of the times the magnitude is to be used.

This leads to the application of the models in deriving discrimination measures.
Besides the above properties, the theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
In view of the models given in Eqns \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution},
  the likelihood test statistics exposed in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
can be simulated as:
\begin{align*}
  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
\end{align*}
where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
As a by-product of this exact derivation, the current paper also proposed several simpler discrimination measures for the common case of $L_x=L_y$.

Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS}, 
new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
These applications however are not included in this paper, but rather left as a suggestion for future investigations.
There are a few reasons for this decision.
The first is that the advantages of the proposed models have been demonstrated through a few applications in this paper:
  the first being a faster ENL evaluation for POLSAR data and
  the second being the visual evaluation of POLSAR speckle filters.
The second reason is that such an application would be quite big in scope, and as such would easily distract the reader from the main proposal of this paper.
Last but not least, this paper focuses on the proposal of several scalar and representative statistical models for POLSAR, which results in associated statistical models and discrimination measures.
It does not, technically speaking, focuses on proposing new discrimination measures.

The advantages of this proposal are thus to be compared against other published models for POLSAR.
Consequently, the methodology to evaluate the result of this proposal is a bit unusual.
While quantitative evaluation is normally employed, in this theoretical model proposal only qualitative evaluation are shown.
This is because compared to existing published observables for POLSAR, the advantage of the proposed observables are qualitative which does not requires numerical quantitative comparisons.
Instead a straightforward binary evaluation would be sufficient.
In comparison to other scalar models for POLSAR, the proposed models for determinant and its log-transformed version are representative are highly representative of the POLSAR data.
This is because these models collapses into the representative SAR intensity when the multi-dimensional data is collapsed into the traditional one-dimensional SAR data.
This is proven in section \ref{sec:sar_special_case_of_polsar}.
No other existing models for POLSAR is known to have this property.

Other advantage is that compared to other proposed scalar models for POLSAR, only these proposed statistical models lead to existing discrimination measures.
This argument is supported by an extensive literature survey in section \ref{sec:lit_review}.
There not only existing published scalar models for POLSAR are reviewed to show that none of them lead to discrimination measure,
  existing discrimination measures for POLSAR are also extensively surveyed leaving virtually no chance of there exists an existing scalar statistical model for POLSAR which leads to existing discrimination measures.

There may have many beneficials implications for this proposal.
One of the main benefits is believed to be that:
  this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
This is illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.  
In evaluating SAR speckle filters, the intensity ratio is widely used.
Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
Assuming a perfect filtering condition, the ratio image should only contain random noise.
Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.

Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
  this technique can be equally applied to evaluate POLSAR speckle filters.
In fact better results can be achieved.
In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
  which is linear and additive in nature.
Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.

@@

Currently while the field of SAR is much more developed than the field of POLSAR,
  the two fields however are quite separated.
Hence many techniques applicable to SAR are not directly applicable to POLSAR.
Under this context, the current proposal provide the bridge between these two separated fields,
  inviting potential extension of various SAR processing techniques to POLSAR data.
For instance the earlier example illustrate that while intensity ratio was commonly used to carry out visually evaluation of SAR speckle filters,
  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
We believe there are many more unexplored possibilities for such applications.

>>>>

\section{Unifying the different discrimination measures proposals for bpth SAR and POLSAR}

At least for both fields of SAR and POLSAR, statistical models have always been the foundation to derive discrimination measures.
For SAR, the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \cite{Rignot_1993_TGRS_896}.
For POLSAR, the same case should apply, 
  except that so far only asymptotic distribution has been derived for the most common foundation, i.e. the likelihood test statistics.
With the insight gained from section \ref{sec:sar_special_case_of_polsar}, 
  it should be clear that the proposed model can also be used to derive discrimination measures for POLSAR.

As a matter of course, in view of the models given in Eqns \ref{eqn:determinant_distribution},
  the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
can be expressed as:
\begin{align*}
  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
\end{align*}
where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.

As a by-product of this exact derivation,
  several discrimination measures for the common case of $L_x=L_y$ are further proposed.
They are the determinant-ratio and the change-ratio presented in Section \ref{sec:theoretical_model}.
Compared to existing discrimination measures for POLSAR reviewed in section \ref{sec:lit_review}, 
  the proposed dissimilarity measures are much simpler.
They, at the same time, are multi-dimensional extensions of the intensity-ratio discrimination measure widely used in SAR.

Thus the core of the proposed approach is that the determinant of the POLSAR covariance matrix is proposed as the scalar and representative observable of the complex and multi-dimensional data.
%What is the novelty of your solution? What are its advantages
Compared to other published scalar observables with accompanying statistical model,
  the proposed observable and its models are highly representative of the multidimensional data.
The representative power of the proposed observable is justified by the following reasons.
Firstly, the covariance matrix determinant, when collapsed into one-dimensional case, transforms neatly into the representative SAR intensity.
Secondly, the statistical model for this observable is shown as the generic multi-dimensional extension of the traditional and representative intensity model for the one dimensional SAR data.
And last but not least, this observable also leads to the determinant-ratio discrimination measure which
  not only is simpler in concept and computation than the existing POLSAR discrimination measures
  but also can be considered as the natural multi-dimensional extension of the commonly-used intensity-ratio discrimination measure in SAR.
% Prof Vun Comment: already mentioned above, no need to repeat
%hai thoughts: actually this should be included to justify our title, and our approach. It is however being moved to discussion / conclusion section
However, before further discussion ensues, 
  it is necessary to validate the presented theoretical model with real-life practical data.

\section{Validating the proposed models against real-life data}
\label{sec:polsar_models_validation}

This section aims to verify the theoretical models given in Eqns. \ref{eqn:determinant_distribution}, \ref{eqn:determinant_ratio_distribution} and \ref{eqn:change_ratio_distribution} against practical data.
All of these models require the estimation of two parameters from the captured data.
These are (i) the dimensional number $d$ and (ii) the look number $L$.
The dimensional number $d$ is related to the type of (POL)SAR data captured,
  with $d=1,2,3$ corresponding to the cases of SAR, partial and full polarimetric SAR data, respectively.
The look-number $L$ can be taken either as nominally stated by the data provider,
  or it can be estimated using the technique proposed by \cite{Anfinsen_2009_TGRS_3795}.

To show the robustness of the proposed models, 
  their validations are also put to test on different types of POLSAR sensors.
Specifically in this paper, the air-borne four-look ($L=4$) AIRSAR image of Flevoland and
  a fine-quad single-look complex RADARSAT2 image ($L=1$) are used.
Since the determinant of the covariance matrix is only significant on multi-look data,
  nine-look processing is first applied on the single-look RADARSAT2 data ($L=9$).

\subsection{The Traditional case of SAR ($d=1$)}

Since it has been shown in Section \ref{sec:sar_special_case_of_polsar} that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
  the validation of the proposed $d=1$ model is quite straightforward. %only a simple validation is presented for this case.  
Fig. \ref{fig:verify_POLSAR_model_1D} presents the results of a test performed for the stated purpose.
In the test, the intensity of single-channel SAR data (HH) for a homogeneous area in both the AIRSAR Flevoland dataset is extracted.
The histograms for both the intensity and intensity ratio %the log-distance and contrast
  are then plotted against the theoretical PDF given above.
Also presented are the plots of the same test applied on a homogeneous patch inside the nine-look processed RADARSAT2 image.
The plots are obtained with ENL set an estimated value obtained using the technique presented in \cite{Anfinsen_2009_TGRS_3795}.
%In this case, even though the RADARSAT2 has a nominal look-number of 9, its ``true'' value is estimated as $L=$ (TODO:CALC).
In all cases, good visual match is apparent, which hence validates the model proposed above. %providing us a simple validation of the result.

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH) determinant]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_determinant}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH) determinant]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_determinant}
	} \\
	\subfloat[AIRSAR (HH) determinant ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH) determinant ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	} \\
	\subfloat[AIRSAR (HH) change ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH) change ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{The specific d=1 models are validated on both practical RADARSAT2 and AIRSAR datasets}
\label{fig:verify_POLSAR_model_1D}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_determinant}
	} 
	\hfill	
	\subfloat[AIRSAR (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}
	\hfill	
	\subfloat[AIRSAR (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}  \\
	\subfloat[RADARSAT2 (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_determinant}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{The specific d=1 models are validated on both practical RADARSAT2 and AIRSAR datasets}
\label{fig:verify_POLSAR_model_1D}
\end{figure}
%endif

\subsection{The Multi-dimensional case of POLSAR ($d=2,3$)}

The remainder of this section now focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
Similar tests %like the one described for SAR data 
  are carried out
  for both types of polarimetric SAR
  on both AIRSAR and RADARSAT2 datasets.
The look-number is estimated for each type of data and for each image using the technique described in \cite{Anfinsen_2009_TGRS_3795}. %and is also noted in the plots.
From the plots, their visual matches again validates the proposed model.

@@

Intuitively, the concept of the determinant being representative of the POLSAR data can be thought of as being similar to the concept of using the magnitude as being representative of a complex number
(in a sense this is also why intensity is widely considered representative of the SAR data complex).
Similar to the determinant, the magnitude observable is also scalar and is not lossless.
To fully represent the complex number, another observable is needed besides the magnitude.
The magnitude however is much more widely used, as it can be shown that it is invariant to a change in the reference frame.
Similarly, the determinant of the POLSAR covariance matrix is also scalar and invariant to a change of polarization basis.
Thus while it is not fully representative of the POLSAR data, it can be said to be highly representative of it.
The important thing is that, it can be used to give a scalar comparison of the multi-dimensional data.
This is also similar to the most commonly used magnitude to compare two or more complex numbers. %, most of the times the magnitude is to be used.

Besides the above properties, the theoretical models may also provide an alternative derivation for the likelihood test statistics widely used in POLSAR.
Similar to the way that different measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS}, 
new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
These applications however are not included in this paper, but rather left as a suggestion for future investigations.
%There are a few reasons for this decision.
%The first is that the advantages of the proposed models have been demonstrated through a few applications in this paper:
%  the first being a faster ENL evaluation for POLSAR data and
%  the second being the visual evaluation of POLSAR speckle filters.
%The second reason is that such an application would be quite big in scope, and as such would easily distract the reader from the main proposal of this paper.
%Last but not least, this paper focuses on the proposal of several scalar and representative statistical models for POLSAR, which results in associated statistical models and discrimination measures.
%It does not, technically speaking, focuses on proposing new discrimination measures.

%The advantages of this proposal are thus to be compared against other published models for POLSAR.
%Consequently, the methodology to evaluate the result of this proposal is a bit unusual.
%While quantitative evaluation is normally employed, in this theoretical model proposal only qualitative evaluation are shown.
%This is because compared to existing published observables for POLSAR, the advantage of the proposed observables are qualitative which does not requires numerical quantitative comparisons.
%Instead a straightforward binary evaluation would be sufficient.
%In comparison to other scalar models for POLSAR, the proposed models for determinant and its log-transformed version are representative are highly representative of the POLSAR data.
%This is because these models collapses into the representative SAR intensity when the multi-dimensional data is collapsed into the traditional one-dimensional SAR data.
%This is proven in section \ref{sec:sar_special_case_of_polsar}.
%No other existing models for POLSAR is known to have this property.
%
%Other advantage is that compared to other proposed scalar models for POLSAR, only these proposed statistical models lead to existing discrimination measures.
%This argument is supported by an extensive literature survey in section \ref{sec:lit_review}.
%There not only existing published scalar models for POLSAR are reviewed to show that none of them lead to discrimination measure,
%  existing discrimination measures for POLSAR are also extensively surveyed leaving virtually no chance of there exists an existing scalar statistical model for POLSAR which leads to existing discrimination measures.

\section{Extending SAR data processing techniques towards POLSAR}

Currently while the field of SAR is much more developed than the field of POLSAR,
  the two fields however are quite separated.
Hence many techniques applicable to SAR are not directly applicable to POLSAR.
With the newly gained, the current proposal provide the bridge between these two separated fields,
  inviting potential extension of various SAR processing techniques to POLSAR data.
%For instance the earlier example illustrate that while intensity ratio was commonly used to carry out visually evaluation of SAR speckle filters,
%  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
%We believe there are many more unexplored possibilities for such applications.

There are many beneficial implications for this proposal.
One of the main benefits is that:
  this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
One example has already been presented in this paper, 
  where existing SAR discrimination measures are extended towards POLSAR.
Another example can be illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.

In evaluating SAR speckle filters, the intensity ratio is widely used.
Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
Assuming a perfect filtering condition, the ratio image should only contain random noise.
Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.

Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
  this technique can be equally applied to evaluate POLSAR speckle filters.
In fact better results can be achieved.
In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
  which is linear and additive in nature.
Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
(TODO: shorten the above 2 paragraphs. 
NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)

@@
